Multiple Kernelized Correlation Filters based High Speed Target Following

### 2017-04-10 draft.tex
Revised the draft to add the submission plan.

A practical solution to target-following mode

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF
\item Re-detection
\item Estimation of geometry between a target and a drone
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Conclusion
\end{itemize}

>>>>

\begin{comment}
Maybe the goal of this work is to public a journal paper about a
practical solution for a drone to follow a single target. For this, we need
\begin{itemize}
\item A vision-based, single target tracking algorithm.
\item Other components for making a drone follow a target.
\begin{itemize}
\item An architecture diagram
\item Descriptions of vehicle control, motion planning, behavior
  generation, estimation of relative geometry between a drone and a
  target, etc
\item Experimental results or example videos
\end{itemize}
\end{itemize}

For the BMVC-17 submission, we're going to just focus on the first
part. This is because we need to build a drone for the second part.
\end{comment}

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF
\item Re-detection for re-initialization
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Conclusion
\end{itemize}
